Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Updates to Lexical Cohesion section and Cohesion structure

In the present research, we investigate the relationship between linguistic
cohesion and social cohesion in times of social conflict and unrest. We tackle a
question related to the one posed by Zeitzoff [-@zeitzoff2017social]: How does 
social media reflect on-the-ground realities during times of social conflict?
To do so, we examine patterns of linguistic cohesion on Twitter during
the Arab Spring uprising in Syria between March and June 2012.

@@

## Lexical cohesion: Connectedness of words
The words that comprise social media posts are the first level at which cohesion
occurs. In Figure 1, we see four sequential tweets, each containing four words.
Each sequential tweet contains some content included in the previous tweets. The
linguistic construct of content word overlap measures the relationship across
units of meaning – here, tweets – where identical and semantically similar words
are repeated [@Graesser_McNamara_Louwerse_Cai_2004]. These repeated lexical
items constitute a theme; on Twitter, this might be a particular hashtag, a
name, a location, or other nominal category. This localized cohesion is
referential; words are repeated and co-referred across tweets, creating a sense
of continuity and cohesiveness of meaning and message.

Lexical cohesion also includes latent semantic analysis (LSA)
[@Graesser_McNamara_Louwerse_Cai_2004. LSA measures semantic similarity across
meaning units using a statistical method called singular value decomposition, an
automated method used to detect plagiarism [@Ceska_2008; @Gamallo_Bordag_2011].
In this process, each meaning unit (tweet) is a weighted vector, and the match
between the tweets is measured as the cosine between the two vectors. This
process provides an empirical relationship between the words used from one tweet
to the next. We identify this as lexical cohesion.

The concept of lexical, or semantic, cohesion has already been applied to the
analysis of political speech, for example the language of Margaret Thatcher, as
well as non-political speech [@Barzilay_Elhadad_1999; @Morris_Hirst_1991].
McNamara and Graesser operationalize the concept of cohesion in their software,
Coh-Metrix, an automated tool that analyzes text and discourse
[@Graesser_Jeon_Yan_Cai_2007; @Graesser_McNamara_Louwerse_Cai_2004;
[@Graesser_McNamara_Kulikowich_2011]. This software generates measures of
co-referential cohesion that captures the amount of overlap in content words (as
opposed to function words, like a, the, and and) in adjacent, local, and global
sentences in the passage. Content word overlap refers to the proportion of words
and word stems that are shared between sentences. A higher proportion of overlap
indicates greater cohesion in the sentence.

In estimating cohesion in Twitter posts, tweets that share content words and
stems will yield higher cohesion values, even amongst speakers with opposing
views on the subject matter. Repetition of terms and concepts is captured by
reiteration, which is a type of lexical cohesion in which a subsequent item
repeats a previous item, or refers to it through synonymous language
[@Halliday_Hasan_1976]. In social media, we can conceive of retweets – reposts
or forwards of previous messages in part or in whole – as a form of reiteration
that increase message cohesion. Since retweets replicate verbatim some part of
another tweet, these tweets would also have higher cohesion. Hashtags function
similarly, and are included in our analysis.

```{r figure-1}

>>>>

In the present research, we investigate the relationship between linguistic
cohesion and social cohesion in times of social conflict and unrest. We tackle a
question related to the one posed by Zeitzoff [-@zeitzoff2017social]: How does 
social media reflect on-the-ground realities during times of social conflict?
To do so, we examine patterns of linguistic cohesion on Twitter and their
connection to real-world events during
the Arab Spring uprising in Syria between March and June 2012.

@@

## Cohesion: A Multi-Leveled, Multi-Layered Concept

### Lexical Cohesion: Connectedness of Words

The concept of lexical, or semantic, cohesion has already been applied to the
analysis of political speech (for example, the language of Margaret Thatcher) 
and non-political speech [@barzilay1999using; @morris1991lexical].

The words that comprise social media posts are the first level at which cohesion
occurs. In Figure \@ref(fig:cohesion-in-tweets), we see four sequential tweets, 
each containing four words.
Each sequential tweet contains some content included in the previous tweets. The
linguistic construct of content word overlap measures the relationship across
units of meaning---here, tweets---where identical and semantically similar words
are repeated [@graesser2004coh]. These repeated lexical
items constitute a theme; on Twitter, this might be a particular hashtag, a
name, a location, or other nominal category. This localized cohesion is
referential; words are repeated and co-referred across tweets, creating a sense
of continuity and cohesiveness of meaning and message.

Typically, these analyses focus on *content words* (e.g., nouns, adjectives,
verbs), which convey more meaningful semantic information than *function words*
(e.g., articles, conjunctions). While function words can provide important
information about complexity and language structure
[@tausczik2010psychological], content words have more specialized meaning and
are therefore more useful when researchers want to understand *what* people are
discussing, rather than *how* they are discussing it [@graesser2004coh;
@mcnamara2014automated].

In estimating cohesion in Twitter posts, tweets that share content words 
will yield higher cohesion values, even among speakers with opposing
views on the subject matter. Repetition of terms and concepts is captured by
reiteration, which is a type of lexical cohesion in which a subsequent item
repeats a previous item, or refers to it through synonymous language
[@halliday1976cohesion]. In social media, we can conceive of retweets (i.e., reposts
or forwards of previous messages) as a form of reiteration
that increase message cohesion. Since retweets replicate verbatim some part of
another tweet, these tweets would also have higher cohesion. Hashtags function
similarly and are included in our analysis.

```{r cohesion-in-tweets, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "Add more informative caption."}
